Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-09-06 analysis/presentation/sim_survey_presentation.Rmd
Add an assumptions slide and revise conclusions

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(crosstalk)
library(raster)
library(lattice)
library(viridis)
library(data.table)
load("analysis/cod_sim_exports/2018-07-13_test/test_output.RData")

@@

@@

- **Sets = primary sampling unit**
    - Only way to improve stratified estimates of total abundance
    - Best way to improve stratified estimates of abundance at age
- **Increasing length sampling does not always improve estimates**
    - At low set densities, more is worse
    - At high set densities, more is better
- **Sampling effort affects both bias and percision**
    - Stratified estimates are supposed to be unbiased?!
    - Likely related to age-specific clustering

@@

Why is there bias? Why is extra sub-sampling ineffective or detrimental?

@@

Increasing sub-sampling effort may be an inefficient means of improving population estimates

- Large catches are relatively infrequent and samples in these sets are not independent
- If the goal is to maximize information, it is likely better to stop collecting psudoreplicates and, instead, focus efforts on other species or the next set

@@

- Taylor to other species and assess sampling protocol
- Add a time component to assess trade-offs / efficiency
- Assess the effects of
    - Missing strata
    - Variable trawl area
- Use this as a platform to test spatial models
- Use as an operating model for an MSE
- Others?

@@

>>>>

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(crosstalk)
library(raster)
library(lattice)
library(viridis)
library(data.table)
load("analysis/cod_sim_exports/2018-09-04_test/test_output.RData")

@@

## Assumptions

>- Population is uniformly distributed within a cell
>- The survey is an instantaneous snapshot of the population
>- Fish are aged at random throughout the division within length bins
>- Ages are estimated without error
>- Trawl dimensions are perfectly standard

@@

- **Sets = primary sampling unit**
    - Only way to improve stratified estimates of total abundance
    - Best way to improve stratified estimates of abundance at age
- **Increasing length sampling does not always improve estimates**
    - At low set densities, more is worse
    - At high set densities, more is better
- **Sampling effort affects both bias and percision**
    - Stratified estimates are supposed to be unbiased?!
    - May be related to age-specific clustering

@@

Why is there bias? Why is extra sub-sampling sometimes useful and sometimes detrimental?

@@

Results suggest that

- Stratified estimates are not always unbiased
- Sets are the most effective way to improve estimates
- Excessive sub-sampling may be detrimental if set density is low

**Caution:** this simple simulation is far from perfect, focuses on one case study, and lacks a cost component

- Makes it difficult to be prescriptive
- Nonetheless, results echo the growing body of literature that concludes
    - Extra sub-sampling is an ineffective means of improving estimates because within-set samples are correlated
    - If the goal is to maximize information, it is likely better to stop collecting psudoreplicates and, instead, focus efforts on other species or the next set

@@

- Taylor to other species and assess sampling protocol
- Add a time component to assess trade-offs / efficiency
- Assess the effects of
    - Missing strata
    - Variable trawl area
    - Random vs. stratified age sampling
- Use this as a platform to test spatial models
- Use as an operating model for an MSE
- Others?

@@

## Code {.smaller}

### Population

```{r, echo = TRUE, eval = FALSE}

      set.seed(438)
      pop <- sim_abundance(ages = 1:20, years = 1:20,
                           R = sim_R(mean = 30000000, log_sd = 0.5,
                                     random_walk = TRUE),
                           Z = sim_Z(mean = 0.5, log_sd = 0.2,
                                     phi_age = 0.9, phi_year = 0.5)) %>%
        sim_distribution(grid = sim_grid(x_range = c(-140, 140), y_range = c(-140, 140),
                                         res = c(3.5, 3.5), shelf_depth = 200,
                                         shelf_width = 100, depth_range = c(0, 1000),
                                         n_div = 1, strat_breaks = seq(0, 1000, by = 20),
                                         strat_splits = 2),
                         ays_covar = sim_ays_covar(sd = 2.8, range = 300,
                                                   phi_age = 0.5, phi_year = 0.9,
                                                   group_ages = 5:20),
                         depth_par = sim_parabola(mu = 200, sigma = 70))

## Code {.smaller}

### Surveys

```{r, echo = TRUE, eval = FALSE}

      surveys <- expand_surveys(set_den = c(0.5, 1, 2, 5, 10) / 1000,
                                lengths_cap = c(5, 10, 20, 50, 100, 500, 1000),
                                ages_cap = c(2, 5, 10, 20, 50))
      sim <- test_surveys(pop,
                          surveys = surveys, n_sims = 5,
                          n_loops = 200, cores = 6,
                          q = sim_logistic(k = 2, x0 = 3),
                          growth = sim_vonB(Linf = 120, L0 = 5, K = 0.1, digits = 0),
                          export = "analysis/cod_sim_exports")
